Approximation as Differentiation

### 2025-05-08 main/formal-structures.tex
Separate doc for notes.

The product/coproduct is called a \emph{biproduct}, and the biproduct structure is denoted by $(\biprod, 0)$.
The unit $0$ is both terminal and initial and is called a \emph{zero} object. A semi-additive category
$\cat{C}$ is enriched in $\CMon$, the category of commutative monoids: for any two morphisms $f, g: X \to Y$
in $\cat{C}$, the biproduct structure provides a way to ``add'' them together, forming a morphism $f + g: X
\to Y$. Diagrammatically:

>>>>

The product/coproduct is called a \emph{biproduct}, and the biproduct structure is denoted by $(\biprod, 0)$.
The unit $0$ is both terminal and initial and is called a \emph{zero} object. \todo{Probably want to state the
biproduct ``laws'' that follow from this formulation.} A semi-additive category $\cat{C}$ is enriched in
$\CMon$, the category of commutative monoids: for any two morphisms $f, g: X \to Y$ in $\cat{C}$, the
biproduct structure provides a way to ``add'' them together, forming a morphism $f + g: X \to Y$.
Diagrammatically:
